Title: A proof-of-concept study

### 2022-01-06 paper.tex
update

To evaluate the simulated photon flux $I$ at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity over line-of-sights from the solar position:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl.
\end{equation}

>>>>

To evaluate the simulated photon flux $I$ at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity over line-of-sights from the solar position at $(x,y,z)=(8,0,0)$ kpc:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl.
\end{equation}
